---
title: "R Notebook"
output: html_notebook
---
#
```{r}
library(tidyverse)
library(reshape2)
library(forcats)
```


Get monthly values of all coin data for 2017
```{r}
md <- read_csv("crypto-markets.csv")
mdsplit <- separate(md,date,c("year","month","day"),sep = "-")
mdsplit$year <- as.integer(mdsplit$year)
md2017 <- select(filter(mdsplit, year == 2017),symbol,month,open,high,low,close,volume,market)
md2017$symbol <- as_factor(md2017$symbol)
md2017$month <- as.integer(md2017$month)
```
Average per month per coin
```{r}
mdmonth <- md2017 %>% 
    group_by(symbol,month) %>% 
    summarize(open = mean(open, na.rm = TRUE),
              high = mean(high, na.rm = TRUE),
              low = mean(low, na.rm = TRUE),
              close = mean(close, na.rm = TRUE),
              market = mean(market, na.rm = TRUE),
              )
```
Now import the reddit monthly data
```{r}
# Import
social1 <-read_csv("words_by_month/results-2017_01.csv") %>% mutate(month = 1)
social2 <-read_csv("words_by_month/results-2017_02.csv") %>% mutate(month = 2)
social3 <-read_csv("words_by_month/results-2017_03.csv") %>% mutate(month = 3)
social4 <-read_csv("words_by_month/results-2017_04.csv") %>% mutate(month = 4)
social5 <-read_csv("words_by_month/results-2017_05.csv") %>% mutate(month = 5)
social6 <-read_csv("words_by_month/results-2017_06.csv") %>% mutate(month = 6)
social7 <-read_csv("words_by_month/results-2017_07.csv") %>% mutate(month = 7)
social8 <-read_csv("words_by_month/results-2017_08.csv") %>% mutate(month = 8)
social9 <-read_csv("words_by_month/results-2017_09.csv") %>% mutate(month = 9)
social10 <-read_csv("words_by_month/results-2017_10.csv") %>% mutate(month = 10)
social11 <-read_csv("words_by_month/results-2017_11.csv") %>% mutate(month = 11)
social12 <-read_csv("words_by_month/results-2017_12.csv") %>% mutate(month = 12)
# Combine
reddit <- bind_rows(social1,social2,social3,social4,social5,social6,social7,social8,social9,social10,social11,social12)

reddit$word <- as_factor(reddit$word)
colnames(reddit)[1] <- "symbol"
reddit$month <- as.integer(reddit$month)
```

Combine the social and market data
```{r}
combined <- mdmonth %>% 
  left_join(reddit) %>% 
  drop_na()
sub <- select(combined,symbol,month,close,s_count)
colnames(sub)[1] <- "coin"
colnames(sub)[3] <- "price"
colnames(sub)[4] <- "mentions"

# normal price and reddit mentions to max per coin
subnorm <- sub %>% 
    group_by(coin) %>% 
    mutate(price = price/max(price),
              mentions = mentions/max(mentions))
```
Get rid of coins without at least 8 months of social media data
```{r}
bycoin <- subnorm %>% 
    group_by(coin) %>% 
    summarise(count = n()) %>% 
    filter(count > 8)

subnormgood <- subnorm %>% 
    filter(coin %in% bycoin$coin)
```
Plot the price and mentions pver time on the same graph.
Red is the price of each coin normailzed to its max value during 2017
BLu is the price of each coin normailzed to its max value during 2017
```{r}
ggplot(subnormgood,aes(x = month, y = relative_value))+
  geom_jitter(aes(y = price),color = "red")+
  geom_smooth(aes(y = price),color = "red")+
  geom_jitter(aes(y = mentions),color = "blue")+
  geom_smooth(aes(y = mentions),color = "blue")
```

